Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-07-08 paper/re-pro-badge.tex
automatically reproduce paper

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/a000fde}{a000fde} at \url{https://github.com/FMatti/Rand-TRACE} on 2024-07-08 at 06:45:20 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/68c3ef6}{68c3ef6} on 2024-07-08 at 18:58:43 UTC.
